\vspace{2cm} \Large \bf Seasonal influenza circulation patterns and future projections

### 2016-02-19 auspice/reports/tex/feb-2016.tex
Fix sampling description.

We base our primary analysis on a set of viruses collected between Feb 2014 and Jan 2016, comprising approximately 100 viruses per month where available and seeking to equilibriate sample counts geographically where possible (Fig.\ \ref{H3N2_counts}). This equilibration attempts to collect equal samples from Africa, China, Europe, Japan/South Korea, North America, Oceania, South America, South Asia, Southeast Asia and West Asia. In the following analysis we collapse samples from China, South Asia, Southeast Asia and West Asia into a single region, resulting in Asia possessing greater sample counts than North America or Europe. The only month that significantly departs from equitable sampling is Jan 2016 with 61 viruses, primarily from Europe and North America. Oct 2015 to Jan 2016 are lacking Southern Hemisphere viruses.

@@

We base our primary analysis on a set viruses collected between Feb 2014 and Feb 2016, comprising approximately 100 viruses per month where available and seeking to equilibriate sample counts geographically where possible. As discussed above, this equilibration attempts to collect equal samples from Africa, China, Europe, Japan/South Korea, North America, Oceania, South America, South Asia, Southeast Asia and West Asia. Recent months through Jan 2016 have largely sufficient sample counts and sample distributions, although are lacking Southern Hemisphere viruses.

>>>>

We base our primary analysis on a set of viruses collected between Feb 2014 and Jan 2016, comprising approximately 100 viruses per month where available and seeking to equilibriate sample counts geographically where possible (Fig.\ \ref{H3N2_counts}). This equilibration attempts to collect equal samples from Africa, China, Europe, Japan/South Korea, North America, Oceania, South America, South Asia, Southeast Asia and West Asia. In the following analysis we collapse samples from China, Southeast Asia, Japan and Korea into a single region that we're calling "East Asia", resulting in East Asia possessing greater sample counts than North America or Europe. The only month that significantly departs from equitable sampling is Jan 2016 with 61 viruses, primarily from Europe and North America. Oct 2015 to Jan 2016 are lacking Southern Hemisphere viruses. We subsample to 100 viruses per month and not more to keep sample counts as equitable as possible across space and time.

@@

We base our primary analysis on a set viruses collected between Feb 2014 and Feb 2016, comprising approximately 100 viruses per month where available and seeking to equilibriate sample counts geographically where possible (Fig.\ \ref{H1N1pdm_counts}). As discussed above, this equilibration attempts to collect equal samples from Africa, China, Europe, Japan/South Korea, North America, Oceania, South America, South Asia, Southeast Asia and West Asia. In the following analysis we collapse samples from China, Southeast Asia, Japan and Korea into a single region that we're calling "East Asia", resulting in East Asia possessing greater sample counts than North America or Europe. Recent months through Jan 2016 have largely sufficient sample counts and sample distributions, although are lacking Southern Hemisphere viruses. We subsample to 100 viruses per month and not more to keep sample counts as equitable as possible across space and time.
